Manuscript 1 code

### 2024-09-14 manuscript_1_code.Rmd
Just trying to avoid problems here

```{r synchrony cover mod}
synch_cov_mod <- glmmTMB(cover_mean ~ synchrony*habitat + (1|site), family = beta_family(), data = diversity_stability_synchrony)
summary(synch_cov_mod)
Anova(synch_cov_mod)
#                     Chisq Df Pr(>Chisq)    
# synchrony         209.545  1  < 2.2e-16 ***
# habitat            52.512  3  2.330e-11 ***
# synchrony:habitat  54.632  3  8.227e-12 ***
hist(residuals(synch_cov_mod)) # slight skew
plot(residuals(synch_cov_mod) ~ fitted(synch_cov_mod)) # same issues as always
emtrends(synch_cov_mod, pairwise ~ habitat, var = "synchrony") # forereef 17 distinct from all other habitats
```

>>>>

```{r synchrony cover mod}
synch_cov_mod <- glmmTMB(cover_mean ~ synchrony*habitat + (1|site), family = beta_family(), data = diversity_stability_synchrony)
summary(synch_cov_mod)
Anova(synch_cov_mod)
#                     Chisq Df Pr(>Chisq)    
# synchrony         209.545  1  < 2.2e-16 ***
# habitat            52.512  3  2.330e-11 ***
# synchrony:habitat  54.632  3  8.227e-12 ***
hist(residuals(synch_cov_mod)) # slight skew
plot(residuals(synch_cov_mod) ~ fitted(synch_cov_mod)) # same issues as always

r.squaredGLMM(synch_cov_mod) # error??
emtrends(synch_cov_mod, pairwise ~ habitat, var = "synchrony") # forereef 17 distinct from all other habitats
```
